---
title: "FIFA Notebook"
output: html_notebook
---

This is an [R ](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code. 

---

### Load the Data
```{r}
library(readr)
FullData <- read_csv("/home/oem/Code/mlprojects/FIFA/more/complete.csv", show_col_types = FALSE)
complement <- read_csv("/home/oem/Code/mlprojects/FIFA/demo/CompleteDataset.csv", show_col_types = FALSE)
df <- read.csv("/home/oem/Code/mlprojects/FIFA/fifa21_male2.csv", stringsAsFactors = FALSE)

```

---

### Summary of the Data
```{r}
library(data.table)
setDT(FullData)
setDT(complemento)
names(FullData)
```
```{r}
dim(FullData)
```
```{r}
library(knitr)
head(FullData)
```

---

### Ages of football players
```{r}
library(ggplot2)
ggplot(FullData, aes(age, fill = age)) + 
geom_bar(position = "stack", color="black", fill= "#39a5f7") 

```

---

### Players' Overall

```{r}
library(dplyr)
FullData %>% 
  ggplot(aes(x = overall, fill = factor(overall))) +
  geom_bar(color = "grey30") + guides(fill = FALSE)+
  labs(title="Player's Overall ")
```

---

### Age vs Rating
```{r}
agerating <- FullData[age<41,.("overall"=mean(overall)),by=age][order(-age)]
agerating
ggplot(data = agerating,aes(x=age,y=overall))+
  geom_line(color="red",size=2)+labs(title="Rating vs Age")+
  annotate("text", x = 30, y = max(agerating$overall),color="blue", label = "Max", parse = TRUE, size = 3)
```

---

### Best Players 
```{r}
library(data.table)
FullData %>%  
  select(name, age,overall,club,eur_value) %>% 
  as.data.table(class = "nowrap hover row-border", escape = FALSE, options = list(dom = 't',scrollX = TRUE, autoWidth = TRUE))
```

---

### Physical Attributes of the Players
#### Height in cm
```{r}
FullData %>% 
  ggplot(aes(x = height_cm)) +
  geom_histogram(binwidth= 1,color = "#72a18b", fill="#72a18b") + 
  labs(title="Players Height")
```
#### Weight in kg
```{r}
FullData %>% 
  ggplot(aes(x = weight_kg)) +
  geom_density(color = "#78081b", fill="lightblue") + 
  geom_vline(aes(xintercept=mean(weight_kg)),
            color="blue", linetype="dashed", size=1)+
  labs(title="Players Weight")
```

#### Height and Weight
```{r}
library(plyr)
mw <- ddply(FullData, "age", summarise, grp.meanw=mean(weight_kg), grp.meanh=mean(height_cm))
ggplot(mw, aes(x=grp.meanw, y=grp.meanh, color = age)) + 
  geom_point(aes()) +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

---

### Wage offered to Players w.r.t Ages
```{r}
d <- FullData[age<40,.("Wage"=mean(eur_wage)),by=age][order(-age)]
ggplot(d, aes(x=age, y=Wage,label = age)) +
  geom_line()+
  geom_point(color= "blue") + 
  geom_text(size =4,hjust=0, vjust=1.3)
```

---

### Nationalities of Players
```{r}
Nationalitys <- FullData[FullData$nationality!="",.N,by=.(nationality,`flag`)][order(-N)]
Nationalitys = Nationalitys[,c(1,3)] 
head(Nationalitys[order(Nationalitys$N, decreasing = TRUE),],10)
```

---

### Best Teams in the Game
#### Best Clubs
```{r}
TeamDF<-arrange(FullData[, list(Avg=mean(overall)), by= "club" ], desc(Avg) ) 
head(TeamDF, 10)
```

---

## Clustering
### Number of Clusters
#### Ward's Method
```{r}
cluster = FullData[,c(7,10,11,17:29,34:94)]
cluster[is.na(cluster)] = 0
wss <- (nrow(cluster[,c()])-1)*sum(apply(cluster[,1:ncol(cluster)],2,var))

for (i in 2:10) 
  wss[i] <- sum(kmeans(cluster[,1:ncol(cluster)], centers=i)$withinss)

plot(1:
       10, wss, type="b", xlab="Number of Cluster",  ylab="Squares Summatory")
```

---

### K Means Clustering
```{r}
library(fpc)
km<-kmeans(cluster[,1:ncol(cluster)],4)
cluster$grupo<-km$cluster
FullData$grupo <-km$cluster
g1<- FullData[FullData$grupo==1,]
g2<- FullData[FullData$grupo==2,]
g3<- FullData[FullData$grupo==3,]
g4<- FullData[FullData$grupo==4,]

plotcluster(cluster[,1:(ncol(cluster)-1)],km$cluster)

```

---

### Player's Overall Ratings according to the groups
```{r}
g1 %>% 
  ggplot(aes(x = overall, fill = factor(overall))) +
  geom_histogram(binwidth=1)+
  labs(title="Player Ratings for Group 1")

g2 %>% 
  ggplot(aes(x = overall, fill = factor(overall))) +
  geom_histogram(binwidth = 1) +
  labs(title="Player Ratings for Group 2")

g3 %>% 
  ggplot(aes(x = overall, fill = factor(overall))) +
  geom_histogram(binwidth=1)+
  labs(title="Player Ratings for Group 3")

g4 %>% 
  ggplot(aes(x = overall, fill = factor(overall))) +
  geom_histogram(binwidth=1)+
  labs(title="Player Ratings for Group 4")

```

### Density of EUR_Value for Players in Groups
```{r}
ggplot(g1, aes(eur_value, fill = eur_value)) +
geom_density(position = "stack", fill = "#5f966e", color = "red")

ggplot(g2, aes(eur_value, fill = eur_value)) +
geom_density(position = "stack", fill = "#5f966e", color = "red")

ggplot(g3, aes(eur_value, fill = eur_value)) +
geom_density(position = "stack", fill = "#5f966e", color = "red")

ggplot(g4, aes(eur_value, fill = eur_value)) +
geom_density(position = "stack", fill = "#5f966e", color = "red")
```

---

### Comparison of Group1 and Group2
```{r}
summary(g1$eur_value)
summary(g2$eur_value)
```


### Comparison of Group3 and Group4
```{r}
summary(g3$eur_value)
summary(g4$eur_value)
```

---

## Machine Learning
### Predicting Position
```{r}
library(caret)
library(plyr)
specs = FullData[,c(22:30,36:67)]
specs = data.frame(specs)

## Specs normalization
specsNorm = preProcess(specs,method = "scale")
specs = predict(specsNorm, specs)
## Adding ID and Overall to Specs
id_overall = FullData[,c(1,20)]
specs = cbind(specs,id_overall)

##Getting preferred_positions and ID
positions = complemento[,c(53,64)]   
positions = data.frame(positions)

## Cleaning Preferred Positions
prefered_positions = positions[,'Preferred.Positions']
split = strsplit(prefered_positions, split=" ")
positionVector = 0
length = length(split)
for (position in 1:length) {
    positionVector[position] <- unlist(split[[position]][1]) 
  }
positions[,'Preferred.Positions'] = positionVector

#Joining data
selected_data = join(specs, positions, by = NULL, type = "full", match = "first") 
selected_data = selected_data[complete.cases(selected_data),]

#Attack or Defense
position = selected_data[,'Preferred.Positions']
attack = c('ST','LW','RW','RM','CM','LM','CAM','CF')
defense = c('CDM','CB','LB','RB','RWB','LWB','GK')
#Replacing
position <- lapply(position, function(x) replace(x,x %in% attack, 1))
position <- lapply(position, function(x) replace(x,x %in% defense, 0))

positionVector = 0
for (i in 1:length(position)){
    positionVector[i] = position[[i]]
}

positionVector = as.numeric(positionVector)

#joining 
selected_data = cbind(selected_data,positionVector)

selected_data <- subset( selected_data, select = -ID )
selected_data[,'Preferred.Positions'] = as.factor(selected_data[,'Preferred.Positions'])

head(selected_data)
```
### Splitting the Data 70/30
```{r}
percent <- 70/100

set.seed(3)

trainRowsNumber<-sample(1:nrow(selected_data),percent*nrow(selected_data))
train<-selected_data[trainRowsNumber,] 
test<-selected_data[-trainRowsNumber,] 

ataque = selected_data[selected_data[,'positionVector'] ==1,-positionVector]
ataque$Preferred.Positions = factor(ataque$Preferred.Positions)
defensa = selected_data[selected_data[,'positionVector'] ==0,-positionVector]
defensa$Preferred.Positions = factor(defensa$Preferred.Positions)

trainRowsNumber<-sample(1:nrow(ataque),percent*nrow(ataque))
trainA<-ataque[trainRowsNumber,] 
testA<-ataque[-trainRowsNumber,] 

trainRowsNumber<-sample(1:nrow(defensa),percent*nrow(defensa))
trainD<-defensa[trainRowsNumber,] 
testD<-defensa[-trainRowsNumber,] 

head(train)
```

### Logistic Regression
```{r}
model<-glm(positionVector~., data = train)
pred<-predict(model,newdata = test)
pred = round(pred)
cfmLR = confusionMatrix(table(pred,test$positionVector))
cfmLR
```

### SVM
#### Attack
```{r}
library(e1071)
model <- svm(Preferred.Positions~. ,data=trainA,kernel = "linear")
prediccion <- predict(model,testA)
cfmSVM<-confusionMatrix(table(prediccion,testA[,'Preferred.Positions']))
cfmSVM
```

#### Defense
```{r}
modelD <- svm(Preferred.Positions~. ,data=trainD,kernel = "linear")
prediccion <- predict(modelD,testD)
cfmSVM<-confusionMatrix(table(prediccion,testD[,'Preferred.Positions']))
cfmSVM
```

---


## Additional Analytics
### Data Manipulation
```{r}
options(repr.matrix.max.cols=150)
library(dplyr)
library(stringr)
library(tidyr)
df2 <- suppressWarnings(df %>% 
    # Remove Retired Players
    separate(Contract, c("Contract1", "Contract2"), sep = " ~ ") %>%
    mutate_at(vars(Contract1:Contract2), funs(as.numeric)) %>%
    filter(Contract1 >= 2020 | Contract2 > 2020 ) %>%
    # Height & Weight Transformation (KG, CM)
    mutate(Height = round(
    as.numeric(str_sub(str_remove_all(Height, '"'), start = 1, end = 1))*30.48 + as.numeric(str_sub(str_remove_all(Height, '"'), start = 3, end = 5))* 2.54
    ),
           Weight = round(as.numeric(str_sub(Weight, start = 1, end = 3)) / 2.204623)) %>%
    # Create Position Class
    mutate(Class = case_when(
        
        BP %in% c("CB", "RB", "LB", "LWB", "RWB", "LCB", "RCB") ~ "Defence",
        BP == "GK" ~ "Goal Keeper",
        BP %in% c("CM", "CDM","CAM","LM","RM", "LAM", "RAM", "LCM", "RCM", "LDM", "RDM") ~ "Midfielder",
        TRUE ~ "Forward"
        
    )) %>%
    # Market Values & Wage
    mutate(
        Values = as.numeric(str_replace_all(str_remove_all(str_remove_all(Value,"€"), "M"), "K", "000")),
        Values = if_else(Values < 1000 , Values * 1000000, Values),
        Wages = as.numeric(str_replace_all(str_remove_all(Wage,"€"), "K", "000"))

    ))


head(df2)
```

---

### Draw Football Pitch
```{r}
pitch <- function(goaltype = c("box", "line", "barca_numbers"), pitch_theme = c("green","blue","night")){
  
  # Check Arguments
  if(is.null(goaltype) | missing("goaltype")){goaltype <- "box"}
  if(is.null(pitch_theme) | missing("pitch_theme")){pitch_theme <- "green"}
  
  # Field Colour
  if(pitch_theme == "green"){
    # Green
    background_color = "#77BD77"
    grass_color = "#77BD77"
    # Dark Green
    #background_color = "#538032"
    #grass_color = "#538032"
    line_color =  "#ffffff"
    goal_color = "#000000"
    
  }else if(pitch_theme == "blue"){
    
    # Blue
    grass_color = "#224C56" 
    line_color =  "#B3CED9" 
    background_color = "#224C56" 
    goal_color = "#15393D"
    
  }else if(pitch_theme == "night"){
    
    # Night
    grass_color = "#202020"
    line_color =  "#797876"
    background_color = "#202020"
    goal_color = "#131313"
  }else{
    return(NULL)
  }
  
  # All Parameters
  # Size of the Field
  ymin <- 0    # Minimum height
  ymax <- 80   # Maximum Width
  xmin <- 0    # Minimum Width
  xmax <- 120  # Maximum Width
  
  # Off-Field Area
  padding <- 5 # Default: 5
  
  # Penalty Area
  boxEdgeDef <- 18
  boxEdgeOff <- 102
  boxEdgeLeft <- 18
  boxEdgeRight <- 62
  
  # Half Field Line
  halfwayline <- 60
  
  # Rectangle in Front of the Goal Inside the Penalty Area
  sixYardDef <- 6
  sixYardOff <- 114
  sixYardLeft <- 30
  sixYardRight <- 50
  
  # Half-Field Circle Parameters
  CentreSpot <- 40
  centreCirle_d <- 20
  
  # Function
  circleFun <- function(center = c(0,0),diameter = 1, npoints = 100){
    r = diameter / 2
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
  }
  
  center_circle <- circleFun(c(halfwayline,CentreSpot),centreCirle_d,npoints = 100)
  
  # Penalty Point
  penSpotDef <- 12
  penSpotOff <- 108
  
  # Theme Argument size: 12
  size <- 12
  
  # Goal Line
  goalPostLeft <- 36
  goalPostRight <- 44
  
  
  # Scratching the Field
  
  plot <- ggplot()+
    
    # 1. Boundaries of the Football Field
    xlim(c(xmin-padding,xmax+padding)) + ylim(c(ymin-padding,ymax+padding))+
    
    # 2. Setting Theme
    theme(
      # 2.1. Removing Texts and Lines on Axes 
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      
      # 2.2. Legend Adjustments
      legend.background = element_rect(fill = background_color, colour = NA), 
      legend.key = element_rect(fill = background_color),
      legend.key.size = unit(1.2,"lines"),
      legend.text = element_text(size = size),
      legend.title=element_text(size=size, face="bold",hjust=0),
      
      # 2.3. Facet Adjustments - Editing Backgrounds and Texts
      strip.background = element_rect(colour = background_color, fill = background_color, size = .5),
      strip.text.y=element_text(colour=background_color,size = size, angle=270),
      strip.text.x=element_text(size=size*1),
      
      # 2.4. Panel Adjustments
      panel.background=element_rect(fill=background_color,colour=background_color),
      panel.grid = element_blank(),
      panel.spacing = element_blank(), 
      
      # 2.5. Plot Adjustments
      plot.background=element_rect(background_color), 
      plot.margin=unit(c(0, 0, 0, 0), "lines"), 
      plot.title=element_text(size=size*1.2)
    )+
    
    # 3. Field Line: Drawing the rectangle 
    geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), fill = NA, colour = line_color)+
    
    # 4. Penalty Area: Drawing the Rectangle
    geom_rect(aes(xmin=xmin, xmax=boxEdgeDef, ymin=boxEdgeLeft, ymax=boxEdgeRight), fill = grass_color, colour = line_color)+ # Sol Ceza Sahası
    geom_rect(aes(xmin=boxEdgeOff, xmax=xmax, ymin=boxEdgeLeft, ymax=boxEdgeRight), fill = grass_color, colour = line_color)+ # Sağ Ceza Sahası
    
    # 5. Half Court Line
    geom_segment(aes(x = halfwayline, y = ymin, xend = halfwayline, yend = ymax),colour = line_color)+
    
    # 6.Rectangle in Front of the Goal Inside the Penalty Area
    geom_rect(aes(xmin=xmin, xmax=sixYardDef, ymin=sixYardLeft, ymax=sixYardRight), fill = grass_color, colour = line_color)+ # Sol
    geom_rect(aes(xmin=sixYardOff, xmax=xmax, ymin=sixYardLeft, ymax=sixYardRight), fill = grass_color, colour = line_color)+ # Sağ
    
    # 7.Half Court Circle
    geom_path(data=center_circle, aes(x=x,y=y), colour = line_color)+
    geom_point(aes(x = penSpotDef , y = CentreSpot), colour = line_color, size = 0.9)+ # Sol
    geom_point(aes(x = penSpotOff , y = CentreSpot), colour = line_color, size = 0.9)+ # Sağ
    
   
    geom_point(aes(x = halfwayline , y = CentreSpot), colour = line_color)+
    
    # Drawing the Penalty Box
    
    annotate("path",
             x = 12 + 10 * cos(seq(-0.3*pi, 0.3*pi, length.out = 30)),
             y = 40 + 10 * sin(seq(-0.3*pi, 0.3*pi, length.out = 30)),
             col = line_color) +
    annotate("path",
             x = (120-12) - 10 * cos(seq(-0.3*pi, 0.3*pi, length.out = 30)),
             y = 40 + 10 * sin(seq(-0.3*pi, 0.3*pi, length.out = 30)),
             col = line_color)
  
  if(goaltype == "box"){
    
    plot <- plot+
      geom_rect(aes(xmin = xmin - 2 , ymin = goalPostLeft, xmax = xmin, ymax = goalPostRight), fill = grass_color, colour = line_color)+
      geom_rect(aes(xmin = xmax, ymin = goalPostLeft, xmax = xmax + 2, ymax = goalPostRight), fill = grass_color, colour = line_color)
    
  }else if(goaltype == "line"){
    
    plot <- plot+
      geom_segment(aes(x = xmin, y = goalPostLeft, xend = xmin, yend = goalPostRight),colour = goal_color, size = 1) + # Sol
      geom_segment(aes(x = xmax, y = goalPostLeft, xend = xmax, yend = goalPostRight),colour = goal_color, size = 1) # Sağ
    
  }else if(goaltype == "barca_numbers"){
    
    plot <- plot+
      geom_segment(aes(x = xmin - 0.75, y = goalPostLeft, xend = xmin - 0.75, yend = goalPostRight),colour = line_color, size = 0.75)+
      geom_segment(aes(x = xmax + 0.75, y = goalPostLeft, xend = xmax + 0.75, yend = goalPostRight),colour = line_color, size = 0.75)
    
  }else{
    return(NULL)
  }
  
  
  
  TopLeftCorner <- circleFun(c(xmin,ymax),2.27,npoints = 50)
  TopRightCorner <- circleFun(c(xmax,ymax),2.27,npoints = 50)
  BottomLeftCorner <- circleFun(c(xmin,ymin),2.27,npoints = 50)
  BottomRightCorner <- circleFun(c(xmax,ymin),2.27,npoints = 50)
  
  plot <- plot+
    geom_path(data=TopLeftCorner %>% filter(x > 0, y < 80) , aes(x=x,y=y), colour = line_color)+
    geom_path(data=BottomLeftCorner %>% filter(x > 0, y > 0) , aes(x=x,y=y), colour = line_color)+
    geom_path(data=TopRightCorner %>% filter(x < 120, y < 80) , aes(x=x,y=y), colour = line_color) +
    geom_path(data=BottomRightCorner %>% filter(x < 120, y > 0) , aes(x=x,y=y), colour = line_color)
  
  
  
  
  return(plot)
}

```
```{r}
library(ggplot2)
pitch()
```


---

### Lionel Messi vs Cristiano Ronaldo
```{r}
library(gridExtra)
library(tibble)
library(dplyr)
library(magrittr)
library(cowplot)
library(sure)
plot_player_ratings <- function(data, player_name)({
    
    player <- data%>%filter(Name == player_name)%>%select(Position, LS:GK)
    # Transform from column to observation
    player <- suppressWarnings(as.data.frame(t(player)) %>% 
      rownames_to_column("Pos") %>% 
      filter(Pos != "Position")%>%
      mutate(V1 = as.numeric(str_sub(V1, end = 2)),
             Pos = as.character(Pos)))

    # Create pitch & positions
    pos <- data.frame(
      Pos = as.character(c("GK","LB","LCB","CB", "RCB","RB",
                          "LWB", "LDM", "CDM", "RDM", "RWB",
                          "LM", "LCM", "CM", "RCM", "RM",
                          "LAM", "CAM", "RAM",
                          "LW","LF","CF","RF","RW",
                          "LS","ST","RS")), 
      x = c(7, rep(20,5), rep(38, 5), rep(55, 5), rep(72, 3), rep(90,5), rep(110,3)),
      y = c(40,rep(c(10, 25, 40,55,70), 3), c(20, 40, 60),c(10, 25, 40, 55,70), c(20, 40, 60)))%>%suppressWarnings()%>%suppressMessages()
    
    # Join player data & pitch
    player <- left_join(player, pos, by = 'Pos')%>%suppressWarnings()%>%suppressMessages()

    # Remove an unnecessary observation
    player <- na.omit(player)%>%suppressWarnings()%>%suppressMessages()
    
    
    p <- pitch(pitch_theme = "blue")+coord_flip()+
        geom_point(player, mapping = aes(x,y, fill = if_else(V1 < 50, "orangered", 
                                        if_else(V1 <60, "orange",
                                                if_else(V1 < 70, "goldenrod1", 
                                                        if_else(V1 <80, "palegreen4",
                                                                if_else(V1 < 90, "forestgreen",
                                                                        if_else(V1 == 0,
                                                                                "orangered","darkgreen"))))))), shape = 21, size = 15, show.legend = FALSE)+
    geom_text(player, mapping = aes(x,y, label = Pos), vjust= -0.5, color = "white", size = 2.5, fontface = "bold")+
    geom_text(player, mapping = aes(x,y, label = V1), vjust = 1.5, fontface = "bold", color = "white")+
    scale_fill_identity()+
    labs(title = paste0(player_name,"'s Overall Ratings on the Pitch"))+
    theme(plot.title = element_text(hjust = 0.5,vjust = -1, size = 10, color = "white", face = "bold"))
    return(p)
    
})
    

options(repr.plot.width = 20, repr.plot.height = 16)    
grid.arrange(
    ggdraw() +
      draw_plot(plot_player_ratings(df, "L. Messi")) +
      draw_image(df%>%filter(Name == "L. Messi")%>%pull(Player.Photo)%>%as.character, scale=0.15, y=0.3, x=-0.34)+
      draw_image(df%>%filter(Name == "L. Messi")%>%pull(Club.Logo)%>%as.character, scale=0.15, y=0.3, x=0.34),
    ggdraw() +
      draw_plot(plot_player_ratings(df, "Cristiano Ronaldo")) +
      draw_image(df%>%filter(Name == "Cristiano Ronaldo")%>%pull(Player.Photo)%>%as.character, scale=0.15, y=0.3, x=-0.34)+
      draw_image(df%>%filter(Name == "Cristiano Ronaldo")%>%pull(Club.Logo)%>%as.character, scale=0.15, y=0.3, x=0.34),
    ncol = 2
    )
     
```
```{r}
players <- df2 %>% 
  filter(Name %in% c("Cristiano Ronaldo", "L. Messi")) %>% 
# Unite Name & Club variables
  mutate(Name = paste0(Name, ", ", Club)) %>%
# Selection abilities of the players
  select(Name,Crossing:Sliding.Tackle, -Mentality, -Power, -Defending, -Skill, -Movement ) %>% 
# Correction of the punctuation
  rename_all(funs(gsub("[[:punct:]]", " ", .))) %>% 
# Transform from Variable to Observation
  gather(Skill, Exp, Crossing:`Sliding Tackle`, -Name)


options(repr.plot.width = 15, repr.plot.height = 8)


ggplot(players, aes(Skill, Exp, fill = Name))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_wrap(Name~.)+
  scale_fill_manual(values = c("#59545c", "#9623e8"))+
  theme_minimal()+
  theme(
      strip.text = element_text(size = 15),
      axis.title = element_text(size = 8),
      axis.text = element_text(size = 8)
  )
```
```{r}
options(repr.plot.width = 15, repr.plot.height = 8)


ggplot(players, aes(Skill, Exp, fill = Name))+
  geom_col(position = "fill")+
  coord_flip()+
  scale_fill_manual(values = c("#26241f", "#eda411"))+
  theme_minimal()+
  theme(
      strip.text = element_text(size = 20),
      axis.title = element_text(size = 13),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 16),
      plot.caption = element_text(size= 10)
  )+
  geom_hline(yintercept = 0.5, color = "white", size = 1, linetype = 2)+
  theme(legend.position = "top", axis.text.x=element_blank())+
  labs(caption = "@EA Sports - FIFA 21",
       fill = NULL,x = NULL, y = NULL)
```